\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-11-29 main.tex
Updates from Overleaf

# Define the device geometry.
length_units = "um"
ro = 3  # outer radius
ri = 1  # inner radius
slit_width = 0.25
Lambda = 1  # effective penetration depth
# circle() and box() generate arrays of polygon (x, y) coordinates.
ring = circle(ro)
hole = circle(ri)
slit = box(slit_width, 1.5 * (ro - ri), center=(0, -(ro + ri) / 2))
# Define the Polygon representing the superconductor.
layer = sc.Layer("base", Lambda=Lambda)
film = sc.Polygon.from_difference(
    [ring, slit, hole], name="ring_with_slit", layer="base"
)
bounding_box = sc.Polygon("bounding_box", layer="base", points=circle(1.2 * ro))
# Create a Device and generate and plot the computational mesh.
device = sc.Device(
    film.name,
    layers=[layer],
    films=[film],
    abstract_regions=[bounding_box],
    length_units=length_units,
)
device.make_mesh(min_points=5000, optimesh_steps=None)
device.plot(mesh=True)
# Calculate the device's response to a uniform applied field.
applied_field = sc.sources.ConstantField(10)
solution = sc.solve(device, applied_field=applied_field, field_units="uT")[-1]
# Visualize the solution.
# Plot the current density evaluated at each layer in the Device.
solution.plot_currents()
# Plot the magnetic field evaluated at each layer in the Device.
solution.plot_fields()
# Plot the field evaluated at any points in space.
solution.plot_field_at_positions(device.points, zs=0.5)
\end{minted}
\captionof{listing}{The typical workflow for a \SuperScreen simulation: 1) Define the device geometry and materials properties, 2) generate the computational mesh, 3) solve the model for a given applied field and/or trapped flux, and 4) visualize the results.}
\label{code:device}
\end{code}

@@

For this reason, mutli-layer structures with closely-spaced layers are the most challenging class of problem to solve. The iterative method used described in Section~\ref{section:model:multilayer} is memory-intensive for models with a large mesh (many vertices $p$ and triangles $t$, with typically $t\approx 2p$) and/or many layers $L$, because the average distance between vertices decreases slowly with increasing number of vertices, $\langle\delta r\rangle\sim p^{-1/2}$, whereas the size of the (dense floating-point) $p\times p$ matrix that represents the dipole kernel $Q_z(\vec{r},\pvec{r}')$ in Eq.~\ref{eq:hz-from-kernel} increases as $p^2$. The end result is that the memory footprint of kernel matrix scales roughly as $\langle\delta r\rangle^{-4}$, so decreasing the mean distance between vertices by a factor of 2 increases the memory required by a factor of 16 (see Figure~\ref{fig:scaling}).
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{examples/images/scaling.pdf}
    \caption{Scaling of kernel matrix size $p^2$ with mesh vertex spacing $\delta r$ for a mesh with $p$ vertices and $t$ triangles. (a) Typically the number of triangle $t$ in the mesh is close to twice the number of vertices $p$. (b) Normalized histograms of vertex distances $\delta r$ (colors correspond to the points in (a)). The histogram bins are given by \inline{numpy.linspace(0.15, 0.65, 201)}. (c) The mean vertex-to-vertex distance $\langle\delta r\rangle$ scales roughly as $p^{-1/2}$. (d). The size of each $p\times p$ kernel matrix (of which where are $\binom{L}{2}$ for a device with $L$ layers) scales roughly as $\langle\delta r\rangle^{-4}$.}
    \label{fig:scaling}
\end{figure}

>>>>

# Define the device geometry.
length_units = "um"
ro = 3  # outer radius
ri = 1  # inner radius
slit_width = 0.25
Lambda = 1  # effective penetration depth
# circle() and box() generate arrays of polygon (x, y) coordinates.
ring = circle(ro)
hole = circle(ri)
slit = box(slit_width, 1.5 * (ro - ri), center=(0, -(ro + ri) / 2))
# Define the Polygon representing the superconductor.
layer = sc.Layer("base", Lambda=Lambda)
film = sc.Polygon.from_difference(
    [ring, slit, hole], name="ring_with_slit", layer="base"
)
bounding_box = sc.Polygon("bounding_box", layer="base", points=circle(1.2 * ro))
# Create a Device and generate and plot the computational mesh.
device = sc.Device(
    film.name,
    layers=[layer],
    films=[film],
    abstract_regions=[bounding_box],
    length_units=length_units,
)
device.make_mesh(min_points=3500, optimesh_steps=None)
device.plot(mesh=True)
# Calculate the device's response to a uniform applied field.
applied_field = sc.sources.ConstantField(10)
solution = sc.solve(device, applied_field=applied_field, field_units="uT")[-1]
# Visualize the solution.
# Plot the current density evaluated at each layer in the Device.
solution.plot_currents()
# Plot the magnetic field evaluated at each layer in the Device.
solution.plot_fields()
# Plot the field evaluated at any points in space.
solution.plot_field_at_positions(device.points, zs=0.5)
\end{minted}
\captionof{listing}{The typical workflow for a \SuperScreen simulation: 1) Define the device geometry and materials properties, 2) generate the computational mesh, 3) solve the model for a given applied field and/or trapped flux, and 4) visualize the results.}
\label{code:device}
\end{code}

@@

For this reason, mutli-layer structures with closely-spaced layers are the most challenging class of problem to solve. The iterative method used described in Section~\ref{section:model:multilayer} is memory-intensive for models with a large mesh (many vertices $p$ and triangles $t$, with typically $t\approx 2p$) and/or many layers $L$, because the average distance between vertices decreases slowly with increasing number of vertices, $\langle\delta r\rangle\sim p^{-1/2}$, whereas the size of the (dense floating-point) $p\times p$ matrix that represents the dipole kernel $Q_z(\vec{r},\pvec{r}')$ in Eq.~\ref{eq:hz-from-kernel} increases as $p^2$. The end result is that the memory footprint of kernel matrix scales roughly as $\langle\delta r\rangle^{-4}$, so decreasing the mean distance between vertices by a factor of 2 increases the memory required by a factor of roughly 16 (see Figure~\ref{fig:scaling}).
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{examples/images/scaling.pdf}
    \caption{Scaling of kernel matrix size $p^2$ with mesh vertex spacing $\delta r$ for a mesh with $p$ vertices and $t$ triangles for the device shown in Figure~\ref{fig:xlarge-dz-dr}. (a) Typically the number of triangle $t$ in the mesh is close to twice the number of vertices $p$. (b) Normalized histograms of vertex distances $\delta r$ (colors correspond to the points in (a)). The histogram bins are given by \inline{numpy.linspace(0.15, 0.65, 201)}. (c) The mean vertex-to-vertex distance $\langle\delta r\rangle$ scales roughly as $p^{-1/2}$. (d). The size of each $p\times p$ kernel matrix (of which where are $\binom{L}{2}$ for a device with $L$ layers) scales roughly as $\langle\delta r\rangle^{-4}$.}
    \label{fig:scaling}
\end{figure}
